---
title: "Amanda Nagle p8105 HW 1"
author: "Amanda Nagle"
output: github_document
---
 

# Problem 1

Here is  my solution to problem 1:

```{r}
library(tidyverse)

#creating the first data frame

df_1 = tibble(
              a = rnorm(10),
              b = a > 0,
              c = c("a", "Character", "vector", "of", "length", "ten", "in", "column", "lettered", "c"),
              d = factor(c("low", "medium", "high",           "low","medium", "high", "low", "medium", "high", "low")))
```
Attempting to take the mean of all columns:
```{r}
summarise_all(df_1,mean)
```
Means can be taken of columns a and b, but columns c and d are not numeric and the mean function cannot be applied to them.

The following code attempts to force columns c and d into numeric form using as.numeric.

```{r eval=FALSE}
mutate_at(df_1, c("b", "c", "d"), as.numeric)
```
Doing some math with the logical variable:
```{r}
df_num_b = mutate(df_1, b = as.numeric(b), e = a * b)
df_factor_b = mutate(df_1, b = as.factor(b), e = a * b)
df_factor_then_num_b = mutate(df_1, b = as.numeric(as.factor(b)), e = a * b)
```
When the logical variable b is numeric, the multiplication can be done.
When the logical variable b is a factor, the data frame is created, but the new column is filled with missing values because multiplication is not meaningful with factors.
When the logical variable is changed to a factor then numeric, the multiplication is possible, but potentially less meaningful because the values are coded 1,2 instead of 0,1 as they are coded when coerced to numeric from logical. 

# Problem 2


```{r}
data("penguins", package = "palmerpenguins")
```
Penguins is a data frame with `r ncol(penguins)` variables and `r nrow(penguins)` rows. The variables are: `r names(penguins)`. Mean flipper length is `r mean(pull(penguins, as.numeric(flipper_length_mm)),na.rm=TRUE)`.

Scatter plot of Bill Length by Flipper Length, grouped by Species
```{r}
penguins_plot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

print(penguins_plot)
  
ggsave(file = "penguins_plot.png")
```
